Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2022-01-15 papers/paper/paper.tex
Figure changes to paper
Some amount of progress on paper - rewrote part of the intro, rewrote the discussion, tweaked the results to be in line with the discussion. Current paper status: terrible but the content is hopefully mostly there. Needs lots of editing.

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{breqn}
\usepackage{color}

\newcommand\davidsays[1]{{\em\color{blue} {\bf DR:} #1}}

@@

%\section*{TODO August 2020}
%\begin{enumerate}
%  \item Get new simulations working !!!!!!!!!!!!!!!!!!!
%  \item Articulate data we fit to
%  \begin{enumerate}
%    \item Velocity -> unbinding rate
%    \item Ratio of leading vs trailing steps -> exponential parameter
%    \item Average step length -> other parameters
%    \item Yildiz weird slope -> sticky rate + binding rate
%    \item Avoid instant rebinds -> sticky rate
%    \item Time to kick from MD??
%    \item efficiency (affects instant rebind)
%  \end{enumerate}
%  \item Do the fit (requires 1 above)
%  \item Could have a fixed binding immunity time rather than sticky rate
%  \paragraph{Advantages of immunity time}
%  \begin{enumerate}
%    \item Might accurately reflect a diffusive escape from an energy well
%  \end{enumerate}
%  \paragraph{Advantages of sticky rate}
%  \begin{enumerate}
%    \item Accurately reflects the dynamics of a chemical process
%  \end{enumerate}
%\end{enumerate}

@@

\davidsays{Discuss each figure, and each parameter (how we got it).}

\davidsays{Fig. \ref{fig:ProbLagPlot} gives us the exponential unbinding constant. Also rerun to get better.

Explain that the bothbound time does not vary by more than X\% regardless of initial $L$ in our model.}

\davidsays{histogram plot.  It shows that we are stepping the right distance, our springs are not too stiff, and our angles work out.  Report the average step length.}

\davidsays{contour plot. Gave us the binding rate and the affinity time.  
Very fast binding required (to get slope right) and need affinity time to avoid instantly rebinding.}

\davidsays{Trajectory plot.  Similar to experiment. The bothbound time determines velocity and depends on ATP.}

@@

%% Dynein has several cofactors which alter its dynamics. For example, the motor's stall force is tripled when exposed to dynactin and Bic2D \cite{yildizdynactin}. This is odd, since the dynactin- and Bic2D-binding site on dynein is on the tail, far from the motor heads.

@@

This mechanochemical cycle of chemical transitions is well supported by evidence \cite{citemore}. However, there is still relatively little known about the dynamic mechanism of domain motion dynein uses to achieve its forward motion by transitioning between these states \cite{lippert}. There exist models theorizing how dynein's domains move during its forward step, such as the winch \cite{} and powerstroke \cite{} models, which can reproduce experimental data \cite{}. However, to our knowledge, no studies exist which use protein dynamics to study if either of these dynamic mechanisms is feasible for the dynein motor to produce. Existing computational models of walking use chemical rate transitions and assume independence of steps, without simulating the precise protein dynamics \cite{}. Molecular dynamics simulations exist, but are of too short a timescale to describe dynein's forward stroke \cite{}. It is necessary to model dynein dynamically at a large timescale using physically realistic protein dynamics to fully understand how feasible models like the winch and powerstroke are. Further, such long-timescale dynamic models could be used to find what elements of dynein are sufficient to produce forward motion. Further, an accurate dynamical model would allow us to test if certain dynamical elements, such as electrostatic interactions with the microtubule \cite{longrangemt}, ring stacking \cite{sarlahmodel}, discrete microtubule binding sites \cite{trottmodel}, or elasticity of the stalk \cite{burgess-paper} are necessary for dynein's walk.

Here we use a Monte Carlo simulation that investigates dynein's inter-step correlations as it moves along the MT. We model cytoplasmic dynein by reducing the mechanochemical cycle into two states: the pre-stroke and post-stroke states. We use cryo-EM data to create rough structural models of these conformers, and impose inter-domain tension and elastic restoring forces to describe the dynamics within each conformer. We then model the state transition as a transition between two equilibria, and use Brownian dynamics to simulate the model's behavior in physically realistic drag and diffusion conditions. This minimal model spontaneously generates a powerstroke-like dynamic mechanism, and uses it to produce bidirectional motion. The model also reproduces several experimental measures, such as step length and the probability of stepping. 
%% velocity and force-mediated directionality control.

\begin{figure}[tbhp]
\centering
%\includegraphics[width=0.8\linewidth]{figures/bothbound-cartoon-simple-new.pdf}
%\includegraphics[width=0.8\linewidth]{figures/onebound-cartoon-simple-new.pdf}
\includegraphics[width=1\linewidth]{figures/equilibrium-positions-final.pdf}
\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.}
\davidsays{FIXME remove spring on binding domain and fix caption.}
 \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free. Angles are measured from the $+\hat{x}$ direction. \textit{Right: } Post-stroke model with both MTBDs bound to microtubule. MTBD angles are relative to $+\hat{x}$ direction, and motor angles are between stalk and tail. Lengths and radii not to scale.}
\label{fig:model}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
%\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Scale model compared with experimental images.} \textit{Left:} Model with angles at pre-stroke equilibrium superimposed over axonemal dynein c heavy chain micrograph in the pre-stroke ADP-Vi-bound state \cite{burgess-paper}. Interdomain lengths and radii scaled to micrograph scale bar. No microtubule is present, so $\theta_{nb}$ is arbitrary. \textit{Right: } Model with angles at pre-stroke equilibrium superimposed over density map of full-length native cytoplasmic dynein with accessory tail proteins (map ID EMD-7000) \cite{grotjahn}. Interdomain lengths and radii scaled to density map.}
\label{fig:micrographs}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    Param & Model & Experimental & Source \\
    \hline
    $L_s$ & $\ls$ nm & $21$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
%    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
    $\theta_t$ & $\eqt$ &  & \\
    $R_t$ & $\radiust$ nm & $4$ nm & \cite{Burgess2003}\\
    $R_m$ & $\radiusm$ nm & $5.5$ nm & \cite{Burgess2003}\\
    $R_b$ & $\radiusb$ nm & $1.25$ nm & \cite{Burgess2003}\\
    \hline
  \end{tabular}
  \caption{Constant parameters used in simulation. $L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers. The $\theta$ parameters are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors. $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii. Parameters used for all simulations unless otherwise noted}
  \label{table:constparams}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{lr}
    Param & Model  \\
    \hline
%    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
    $c_m$ & $\cm \Delta G_{ATP}$  \\
    $c_t$ & $\ct \Delta G_{ATP}$  \\
    $k_a$ & $\kstk$  $s^{-1}$  \\
    $k_b$ & $\kb$  nm $s^{-1}$  \\
    $\epsilon$ &  $\MTbindingdistance$ nm  \\
    $k_{ub}$ & $\kub$ $s^{-1}$  \\
    $C$ & $\cexp$  \\
    \hline
  \end{tabular}
  \caption{Free parameters used in simulation. $c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively. $k_a$ is the affinity transition rate from high to low affinity when MTBD unbinds. $k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively. $\epsilon$ is the vertical position allowed for rebinding. $C$ is the tension-gating factor.}
  \label{table:params}
\end{table}

\section{Model}
This model is meant to capture the coarse-grained structural, dynamical and chemical properties of the full dynein complex, while remaining mathematically simple. The structural features of dynein are captured through a two-dimensional geometric model of circular domains connected by rigid rods, shown in Figure \ref{fig:model}. The dynamics of dynein are simulated by imposing both equilibrium and Brownian forces on each circular domain of the model. The chemical properties of dynein are emulated by sporadically transitioning the model between two states: a poststroke state where both binding domains are fixed to the microtubule, and a prestroke state where one foot is free to diffuse. This was influenced by similar simulations done before \cite{zhaomodel}. The poststroke state is meant to represent dynein after rebinding free MTBD and undergoing the motor-MTBD conformational change, but before releasing ADP, according to the Tsygankov scheme \cite{tsygankovscheme}. The prestroke state represents the dynein after binding ATP, unbinding from the MT and undergoing a motor conformational change, but before rebinding the MT. ATP hydrolysis and Pi rejection are ignored by the model. These two states were chosen because ADP release is thought to be the rate limiting step for the whole cycle \cite{holzbaur1989}, and the post-unbinding conformational change is expected to happen soon after MT unbinding \cite{mogamirate}, meaning the post-unbinding conformation should dominate when unbound from MT. We constrain our model to move through only the most likely mechanochemical cycle according to \textit{Tsygankov et al} \cite{tsygankovscheme}, where a head remains in the ADP-bound post-stroke state while the other head goes through the entire mechanochemical cycle, neglecting other possible cycles. Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the cycle \cite{burgess-paper, burgessknight}. In particular, the equilibrium angles governing a tail-motor-MTBD angle change cause a displacement of the free MTBD towards the MT minus end, producing a forward step.

\subsection*{Model geometry}
The dynein model represents a full dynein complex consisting of two dynein heavy chains dimerized by a large tail domain. The model accounts for the following domains within the complex: two microtubule binding domains (``MTBD''), two AAA+ heptad motor domains, and a tail domain consisting of many dynein light chains and a dimerization site. MTBDs, motor domains and the tail are all represented by circles of radius $R_b$, $R_m$ and $R_t$, respectively. Each MTBD is connected to a motor domain via a rigid rod of length $L_s$, meant to represent the stalk domain. Each motor domain is connected to the tail domain via a rigid rod of length $L_t$; this rod represents the heavy chain linker and intermediate/light chains which connect the motor to the dimerization site.

@@

\davidsays{Maybe we want to discuss right here the likely step sizes for leading and trailing steps \emph{if it goes to its equilibrium configuration}.  It's pretty simple and can serve as a ``validation" of our model geometry.}

\subsection*{Equilibrium forces}
The prestroke state has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$. The poststroke state has two: $\theta_{nm}$ and $\theta_{fm}$. The model is free to vary across all of these degrees of freedom, depending on its state, barring steric interactions with the microtubule. These angles describe a planar model which is not capable of transverse motion. To capture the gross dynamics and interdomain oscillations of the protein, restoring forces are imposed on each angle about equilibrium angles $\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for prestroke and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for poststroke. Each domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$ which exerts a restoring force pushing it back to equilibrium, where $c_b$, $c_m$ and $c_t$ are spring constants for each domain. These equilibrium angles are taken to be the average angle occupied by the protein in solution, and are thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}. These angles were extracted from axonemal dynein, but structural similarity suggests they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}. Electron microscopy studies using ADP-Vi to freeze dynein in the pre-stroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.

\subsection*{Binding}
Conformational changes on nucleotide binding, also known as the mechanochemical cycle \cite{cianfrocco}, are captured by transitioning the model between the prestroke and poststroke states. During prestroke, the free MTBD must first release from the MT by transitioning from high to low affinity. The affinity transition rate, $k_a$, governs this process. Binding can then occur when the prestroke model's unbound foot diffuses near enough the microtubule. When within a distance of $\epsilon$, binding occurs at a rate of $k_b$ (Table \ref{table:params}). On binding, the prestroke model changes state to a poststroke model while retaining the positions of its domains. The previously unbound domain is transported to the microtubule.

\subsection*{Unbinding}
Unbinding occurs when a poststroke MTBD unbinds from the microtubule. This event can occur for either MTBD, and each domain has its own unbinding rate $k_{ub}$. To account for the tension-gating proposed by Yildiz \textit{et al} \cite{yildizcleary}, we bias forward directionality by influencing a MTBD to unbind based on the separation distance with the opposing MTBD. For domain $i \in \{n, f\}$ with binding domain angle $\theta_{ib}\left(\theta_{nm}, \theta_{fm}\right)$, unbinding rate is given by $\rho_{ub} = k_{ub}e^{-C\left(\theta_{ib}-\theta^{eq}_{ib}\right)}$, where $C$ is a parameter of the model. This will bias the model to unbind more preferentially for the lagging MTBD due to a higher likelihood for $\theta^{eq}_{ib} > \theta_{ib}$ for the lagging head. Values used for parameters $k_{ub}$ and $C$, along with $k_a$ and $k_b$, are shown in Table \ref{table:params}.

@@

\subsection*{Brownian dynamics}
Brownian dynamics is used to study the model's dynamics in a biophysical manner. In the Brownian regime, protein motion is given by $\dot{\vec{X}} = \frac{1}{\gamma}\left(\vec{F}+\vec{R}\right)$. In the model, each circular domain has its own associated $\gamma$ factor given by Stokes' Law as $\gamma_i = 6\pi\nu R_i$ with dynamic viscosity $\nu$ \cite{stokeslaw}. The force on each domain is given by $\vec{F} = \vec{F}_{spr} + \vec{T}$, where $\vec{T}$ is the tension force between domains maintaining the rigid rod constraint. Each domain feels not only a harmonic restoring force, but also a Brownian force $\vec{R}$. This force is a Gaussian-distributed zero-mean magnitude with variance $R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}$ and uniformly random direction.

\subsection*{Monte Carlo}
A Monte Carlo algorithm governs the simulation of the step. We initialize a two-headed bound configuration of dynein by randomly picking domain angles and calculating the total harmonic energy by summing the energies of each domain. A probability of unbinding, $P_{ub}$, is then calculated from a Boltzmann distribution, where $P_{ub}\propto e^{-\beta E_{total}}$. If dynein unbinds, then the configuration transitions into the one-headed bound state where Brownian dynamics is performed. This process is repeated to generate an ensemble of independent configurations which takes a single step and contributes to a large sample of stepping staistics. A partition function, $Z=\sum e^{-\beta E{total}}$, can then calculate ensemble averages of unbinding rates and probability.

@@

\section*{Prestroke motion equations derivation}
Brownian Dynamics was used to describe the motion of each domain, indexing with $i \in \{bb, bm, t, um, ub\}$, corresponding to bound-binding, bound-motor, tail, unbound-motor, unbound-binding:

@@

\section*{Poststroke motion equations derivation}
Brownian dynamics was initially used for the postroke case but was later changed to be simulated with Monte Carlo methods. After running simulations undergoing Brownian dynamics for both states, we saw a large time spent in this poststroke state causing it to frequently reach equilibrium and be independent of our dynein's stepping pattern. We decided to shorten this process by simulating this state with Monte Carlo algorithms that sample from a Boltzmann distribution of the dynein's total energy. 
*Talk about choosing random configuration of dynein and calculating its total energy from each conformer. 
%% Brownian dynamics was also used for the poststroke case. Due to the added constraint of both binding domains being fixed to the microtubule, the model is fully described by angles $\theta_{nm}$ and $\theta_{fm}$; see Figure \ref{fig:model}. The positions of non-bound domains are defined by the following equation for $i \in \{nb, nm, t, fm, fb\}$, corresponding to near-binding, near-motor, tail, far-motor and far-binding domains:

@@

%
%\subsection*{$c_m$, $c_t$}
The motor and tail spring constants, $c_m$ and $c_t$, relates to the tendency for equilibrium positions in the 1-HB and 2-HB state. We picked these parameters in accordance to the model's ability to perform the powerstroke and achieve processive motion. With these spring constants, the model dynein preferred forward steps towards the minus-end rather than backward steps, while still maintaining flexibility within the stalk and stapping variance.

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{breqn}
\usepackage{color}
\usepackage{subcaption}

\newcommand\davidsays[1]{{\em\color{blue} {\bf DR:} #1}}
\newcommand\forjin[1]{{\em\color{green} {\bf Jin:} #1}}
\newcommand\todo[1]{{\em\color{red} #1}}

@@

\section*{TODO August 2020}
\begin{enumerate}
  \item Articulate data we fit to
  \begin{enumerate}
    \item Velocity -$\>$ unbinding rate
    \item Ratio of leading vs trailing steps -> exponential parameter
    \item Average step length -> other parameters
    \item Yildiz weird slope -> sticky rate + binding rate
    \item Avoid instant rebinds -> sticky rate
    \item Time to kick from MD??
    \item efficiency (affects instant rebind)
  \end{enumerate}
  \item Do the fit (requires 1 above)
  \paragraph{Advantages of sticky rate}
  \begin{enumerate}
    \item Accurately reflects the dynamics of a chemical process
  \end{enumerate}
\end{enumerate}

\section*{TODO January 2022}
\begin{enumerate}
\item go through and fill in missing citations
\item add more paper citations to Discussion, should tie in with more recent science. There are plenty of good uncited papers in the bibtex (10+)  
\item go through model papers and make sure none of them handle correlated stepping, since this is an impt claim we make in the intro
\item heavily edit to make it sound better, probably pretty bad right now
  \item meet with David at some point to see what he thinks
\end{enumerate}

\section*{Notes}
\begin{enumerate}
\item In my head the journal target would be Biophysical Journal; they're pretty open to modeling papers and dynein and one of the dynein modeling papers we cite was published there
\end{enumerate}

\section*{DR}
\davidsays{Fig. \ref{fig:ProbLagPlot} gives us the exponential unbinding constant. Also rerun to get better.
Explain that the bothbound time does not vary by more than X\% regardless of initial $L$ in our model.}

@@

@@

@@

One open question is whether cytoplasmic dynein's structure and mechanochemical cycle are sufficient to explain its stepping behavior. Several modeling studies have addressed this question \cite{alltheorypapers}. \todo{These studies have explained X, and Y, and Z phenomena}. However, to our knowledge no studies have fully explained the dynamics of dynein's step; that is, they haven't explained how dynein's highly variant stepping pattern arises. In addition, dynein is known to have correlation structure between its steps, where the interhead separation of one step influences the step length of the next step \cite{}; this has not been explained by existing models either. Tension gating has been proposed to explain how interhead separation influences step length \cite{}. However, this mechanism doesn't explain how lagging steps are forward directed and leading steps are backward direced, only the relative likelihood of unbinding. Further, it hasn't been explained exactly how dynein manages to step backward and forward, and whether dynein's size and domain flexibility are sufficient to explain this. We put forward that these phenomena can be explained simply by the elastic forces imposed by a dynein motor's domains, and the influence of conformational changes from teh conformational cycle, biasing the diffusive search of the unbound microtubule binding domain. Lagging steps tend to have motor domains positioned relatively forward, biasing the MTBD forward; leaing steps similarly bias teh MTBD diffusion backwards. Backward and forward stepping come from the relatively loose coordination of dynein's domains relative to the strength of Brownian forces on those domains.

Because this explanation requires an accurate model of both the positioning and interdomain forces in cytoplasmic dynein, to test it we created a detailed model of dynein capturing both the structural relationships between the primary domains in the motor, and also the interdomain tension and elasticity forces acting on each domain. We used Brownian dynamics to simulate the diffusive search the motor undergoes as its head unbind and rebind the microtubule. Here we report results demonstrating that such a model is capable of reproducing both the varied, forward-and-backward stepping pattern of dynein, and also the interstep correlation.

%This mechanochemical cycle of chemical transitions is well supported by evidence \cite{citemore}. However, there is still relatively little known about the dynamic mechanism of domain motion dynein uses to achieve its forward motion by transitioning between these states \cite{lippert}. There exist models theorizing how dynein's domains move during its forward step, such as the winch \cite{} and powerstroke \cite{} models, which can reproduce experimental data \cite{}. However, to our knowledge, no studies exist which use protein dynamics to study if either of these dynamic mechanisms is feasible for the dynein motor to produce. Existing computational models of walking use chemical rate transitions and assume independence of steps, without simulating the precise protein dynamics \cite{}. Molecular dynamics simulations exist, but are of too short a timescale to describe dynein's forward stroke \cite{}. It is necessary to model dynein dynamically at a large timescale using physically realistic protein dynamics to fully understand how feasible models like the winch and powerstroke are. Further, such long-timescale dynamic models could be used to find what elements of dynein are sufficient to produce forward motion. Further, an accurate dynamical model would allow us to test if certain dynamical elements, such as electrostatic interactions with the microtubule \cite{longrangemt}, ring stacking \cite{sarlahmodel}, discrete microtubule binding sites \cite{trottmodel}, or elasticity of the stalk \cite{burgess-paper} are necessary for dynein's walk.

%Here we use a Monte Carlo simulation that investigates dynein's inter-step correlations as it moves along the MT. We model cytoplasmic dynein by reducing the mechanochemical cycle into two states: the pre-stroke and post-stroke states. We use cryo-EM data to create rough structural models of these conformers, and impose inter-domain tension and elastic restoring forces to describe the dynamics within each conformer. We then model the state transition as a transition between two equilibria, and use Brownian dynamics to simulate the model's behavior in physically realistic drag and diffusion conditions. This minimal model spontaneously generates a powerstroke-like dynamic mechanism, and uses it to produce bidirectional motion. The model also reproduces several experimental measures, such as step length and the probability of stepping. 
%% velocity and force-mediated directionality control.

\begin{figure}[tbhp]
\centering
\includegraphics[width=1\linewidth]{figures/equilibrium-positions-final.pdf}
\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.}
 \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free. Angles are measured from the $+\hat{x}$ direction. \textit{Right: } Post-stroke model with both MTBDs bound to microtubule. MTBD angles are relative to $+\hat{x}$ direction, and motor angles are between stalk and tail. Lengths and radii not to scale.}
\label{fig:model}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
%% \includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Scale model compared with experimental images.} \textit{Left:} Model with angles at pre-stroke equilibrium superimposed over axonemal dynein c heavy chain micrograph in the pre-stroke ADP-Vi-bound state \cite{burgess-paper}. Interdomain lengths and radii scaled to micrograph scale bar. No microtubule is present, so $\theta_{nb}$ is arbitrary. \textit{Right: } Model with angles at pre-stroke equilibrium superimposed over density map of full-length native cytoplasmic dynein with accessory tail proteins (map ID EMD-7000) \cite{grotjahn}. Interdomain lengths and radii scaled to density map.}
\label{fig:micrographs}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    Param & Model & Experimental & Source \\
    \hline
    $L_s$ & $\ls$ nm & $21$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
    $\theta_t$ & $\eqt$ &  & \\
    $R_t$ & $\radiust$ nm & $4$ nm & \cite{Burgess2003}\\
    $R_m$ & $\radiusm$ nm & $5.5$ nm & \cite{Burgess2003}\\
    $R_b$ & $\radiusb$ nm & $1.25$ nm & \cite{Burgess2003}\\
    \hline
  \end{tabular}
  \caption{Constant parameters used in simulation. $L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers. The $\theta$ parameters are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors. $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii. Parameters used for all simulations unless otherwise noted}
  \label{table:constparams}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{lr}
    Param & Model  \\
    \hline
    $c_b$ & $\cb \Delta G_{ATP}$ \\
    $c_m$ & $\cm \Delta G_{ATP}$  \\
    $c_t$ & $\ct \Delta G_{ATP}$  \\
    $k_a$ & $\kstk$  $s^{-1}$  \\
    $k_b$ & $\kb$  nm $s^{-1}$  \\
    $\epsilon$ &  $\MTbindingdistance$ nm  \\
    $k_{ub}$ & $\kub$ $s^{-1}$  \\
    $C$ & $\cexp$  \\
    \hline
  \end{tabular}
  \caption{Free parameters used in simulation. $c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively. $k_a$ is the affinity transition rate from high to low affinity when MTBD unbinds. $k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively. $\epsilon$ is the vertical position allowed for rebinding. $C$ is the tension-gating factor.}
  \label{table:params}
\end{table}

\section*{Model}
This model is meant to capture the coarse-grained structural, dynamical and chemical properties of the full dynein complex, while remaining mathematically simple. The structural features of dynein are captured through a two-dimensional geometric model of circular domains connected by rigid rods, shown in Figure \ref{fig:model}. The dynamics of dynein are simulated by imposing both equilibrium and Brownian forces on each circular domain of the model. The chemical properties of dynein are emulated by sporadically transitioning the model between two states: a poststroke state where both binding domains are fixed to the microtubule, and a prestroke state where one foot is free to diffuse. This was influenced by similar simulations done before \cite{zhaomodel}. The poststroke state is meant to represent dynein after rebinding free MTBD and undergoing the motor-MTBD conformational change, but before releasing ADP, according to the Tsygankov scheme \cite{tsygankovscheme}. The prestroke state represents the dynein after binding ATP, unbinding from the MT and undergoing a motor conformational change, but before rebinding the MT. ATP hydrolysis and Pi rejection are ignored by the model. These two states were chosen because ADP release is thought to be the rate limiting step for the whole cycle \cite{holzbaur1989}, and the post-unbinding conformational change is expected to happen soon after MT unbinding \cite{mogamirate}, meaning the post-unbinding conformation should dominate when unbound from MT. We constrain our model to move through only the most likely mechanochemical cycle according to \textit{Tsygankov et al} \cite{tsygankovscheme}, where a head remains in the ADP-bound post-stroke state while the other head goes through the entire mechanochemical cycle, neglecting other possible cycles. Each state feels equilibrium forces on its domains meant to mimic the structural changes which occur during the cycle \cite{burgess-paper, burgessknight}. In particular, the equilibrium angles governing a tail-motor-MTBD angle change cause a displacement of the free MTBD towards the MT minus end, producing a forward step.

\subsubsection*{Model geometry}
The dynein model represents a full dynein complex consisting of two dynein heavy chains dimerized by a large tail domain. The model accounts for the following domains within the complex: two microtubule binding domains (``MTBD''), two AAA+ heptad motor domains, and a tail domain consisting of many dynein light chains and a dimerization site. MTBDs, motor domains and the tail are all represented by circles of radius $R_b$, $R_m$ and $R_t$, respectively. Each MTBD is connected to a motor domain via a rigid rod of length $L_s$, meant to represent the stalk domain. Each motor domain is connected to the tail domain via a rigid rod of length $L_t$; this rod represents the heavy chain linker and intermediate/light chains which connect the motor to the dimerization site.

@@

\subsubsection*{Equilibrium forces}
The prestroke state has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$. The poststroke state has two: $\theta_{nm}$ and $\theta_{fm}$. The model is free to vary across all of these degrees of freedom, depending on its state, barring steric interactions with the microtubule. These angles describe a planar model which is not capable of transverse motion. To capture the gross dynamics and interdomain oscillations of the protein, restoring forces are imposed on each angle about equilibrium angles $\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for prestroke and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for poststroke. Each domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$ which exerts a restoring force pushing it back to equilibrium, where $c_b$, $c_m$ and $c_t$ are spring constants for each domain. These equilibrium angles are taken to be the average angle occupied by the protein in solution, and are thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}. These angles were extracted from axonemal dynein, but structural similarity suggests they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}. Electron microscopy studies using ADP-Vi to freeze dynein in the pre-stroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.

The rigid rod geometry and equilibrium angles can be used to calculate the mean step size. If all joints except the tail joint are treated as rigid, then two steps are possible: a forward step of $6.3$nm and a backwards step of $73$nm. This serves as a validation of the geometry of the model, which reproduces the experimental mean step size of XYZ \cite{xyz}.

\subsubsection*{Binding}
Conformational changes on nucleotide binding, also known as the mechanochemical cycle \cite{cianfrocco}, are captured by transitioning the model between the prestroke and poststroke states. During prestroke, the free MTBD must first release from the MT by transitioning from high to low affinity. The affinity transition rate, $k_a$, governs this process. Binding can then occur when the prestroke model's unbound foot diffuses near enough the microtubule. When within a distance of $\epsilon$, binding occurs at a rate of $k_b$ (Table \ref{table:params}). On binding, the prestroke model changes state to a poststroke model while retaining the positions of its domains. The previously unbound domain is transported to the microtubule.

\subsubsection*{Unbinding}
Unbinding occurs when a poststroke MTBD unbinds from the microtubule. This event can occur for either MTBD, and each domain has its own unbinding rate $k_{ub}$. To account for the tension-gating proposed by Yildiz \textit{et al} \cite{yildizcleary}, we bias forward directionality by influencing a MTBD to unbind based on the separation distance with the opposing MTBD. For domain $i \in \{n, f\}$ with binding domain angle $\theta_{ib}\left(\theta_{nm}, \theta_{fm}\right)$, unbinding rate is given by $\rho_{ub} = k_{ub}e^{-C\left(\theta_{ib}-\theta^{eq}_{ib}\right)}$, where $C$ is a parameter of the model. This will bias the model to unbind more preferentially for the lagging MTBD due to a higher likelihood for $\theta^{eq}_{ib} > \theta_{ib}$ for the lagging head. Values used for parameters $k_{ub}$ and $C$, along with $k_a$ and $k_b$, are shown in Table \ref{table:params}.

@@

\subsubsection*{Brownian dynamics}
Brownian dynamics is used to study the model's dynamics in a biophysical manner. In the Brownian regime, protein motion is given by $\dot{\vec{X}} = \frac{1}{\gamma}\left(\vec{F}+\vec{R}\right)$. In the model, each circular domain has its own associated $\gamma$ factor given by Stokes' Law as $\gamma_i = 6\pi\nu R_i$ with dynamic viscosity $\nu$ \cite{stokeslaw}. The force on each domain is given by $\vec{F} = \vec{F}_{spr} + \vec{T}$, where $\vec{T}$ is the tension force between domains maintaining the rigid rod constraint. Each domain feels not only a harmonic restoring force, but also a Brownian force $\vec{R}$. This force is a Gaussian-distributed zero-mean magnitude with variance $R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}$ and uniformly random direction.

\subsubsection*{Monte Carlo}
A Monte Carlo algorithm governs the simulation of the step. We initialize a two-headed bound configuration of dynein by randomly picking domain angles and calculating the total harmonic energy by summing the energies of each domain. A probability of unbinding, $P_{ub}$, is then calculated from a Boltzmann distribution, where $P_{ub}\propto e^{-\beta E_{total}}$ (\todo{is this right? we don't use just the binding angle?}). If dynein unbinds, then the configuration transitions into the one-headed bound state where Brownian dynamics is performed. This process is repeated to generate an ensemble of independent configurations which takes a single step and contributes to a large sample of stepping staistics. A partition function, $Z=\sum e^{-\beta E{total}}$, can then calculate ensemble averages of unbinding rates and probability. \todo{maybe a bit more info on how you go from binding to unbinding over the course of a single simulation, especially wrt L; readers may not know how this works}

@@

\subsubsection*{Prestroke motion equations derivation}
Brownian Dynamics was used to describe the motion of each domain, indexing with $i \in \{bb, bm, t, um, ub\}$, corresponding to bound-binding, bound-motor, tail, unbound-motor, unbound-binding:

@@

\subsubsection*{Poststroke motion equations derivation}
Brownian dynamics was initially used for the postroke case but was later changed to be simulated with Monte Carlo methods. After running simulations undergoing Brownian dynamics for both states, we saw a large time spent in this poststroke state causing it to frequently reach equilibrium and be independent of our dynein's stepping pattern. We decided to shorten this process by simulating this state with Monte Carlo algorithms that sample from a Boltzmann distribution of the dynein's total energy. 
*Talk about choosing random configuration of dynein and calculating its total energy from each conformer. 
%% Brownian dynamics was also used for the poststroke case. Due to the added constraint of both binding domains being fixed to the microtubule, the model is fully described by angles $\theta_{nm}$ and $\theta_{fm}$; see Figure \ref{fig:model}. The positions of non-bound domains are defined by the following equation for $i \in \{nb, nm, t, fm, fb\}$, corresponding to near-binding, near-motor, tail, far-motor and far-binding domains:

@@
